Learning Features and Abstract Actions for Computing Generalized Plans

### 2018-11-08 doc/camera-ready/paper.tex
spellcheck

Different assignments $\sigma$ give rise to different features $F_{\sigma}$
and abstract actions $A_{\sigma}$. More meaningful features are found by looking for
satisfying assignments $\sigma$ that minimize a cost measure such as $|F_{\sigma}|$
or, more generally, $\sum_{f \in F_{\sigma}} cost(f)$. We achieve this by casting our problem
into a constrained optimization problem, and more especifically, a Weighted Max-SAT problem,
where clauses resulting from the theories $T$ or $T_G$ are taken as \emph{hard} clauses
and \emph{soft} unit clauses $\neg selected(f)$ are added with  weights $cost(f)$
for all $f \in \F$.

@@

\noindent \textbf{Acknowledgements.}
H. Geffner is partially funded by grant TIN-2015-67959-P, MINECO, Spain.

>>>>

Different assignments $\sigma$ give rise to different features $F_{\sigma}$
and abstract actions $A_{\sigma}$. More meaningful features are found by looking for
satisfying assignments $\sigma$ that minimize a cost measure such as $|F_{\sigma}|$
or, more generally, $\sum_{f \in F_{\sigma}} cost(f)$. We achieve this by casting our problem
into a constrained optimization problem, and more specifically, a Weighted Max-SAT problem,
where clauses resulting from the theories $T$ or $T_G$ are taken as \emph{hard} clauses
and \emph{soft} unit clauses $\neg selected(f)$ are added with  weights $cost(f)$
for all $f \in \F$.

@@

\noindent \textbf{Acknowledgements.}
H. Geffner is partially funded by grant TIN-2015-67959-P, MINECO, Spain.
G. Franc\`{e}s is funded by the European Research Council project ``State Space Exploration: Principles, Algorithms and Applications''.
